Loop Invariant Code Motion in PyPy's Tracing JIT

### 2011-06-13 talk/iwtc11/paper.tex
add myself as an author
add XXX
another xxx

\authorinfo{Hakan Ardo XXX}
           {Affiliation1}
           {hakan@debian.org}
\authorinfo{Carl Friedrich Bolz}
           {Heinrich-Heine-Universität Düsseldorf}
           {cfbolz@gmx.de}

@@

@@

\subsection{Heap Caching}
The objective of heap caching is to remove \lstinline{get} and
\lstinline{set} operations whose results can be deduced from previous
\lstinline{get} and \lstinline{set} operations. Exact details of the
process are outside the scope of this paper. We only consider the interaction
with loop peeling.

>>>>

\authorinfo{Hakan Ardo XXX}
           {Affiliation1}
           {hakan@debian.org}
\authorinfo{Carl Friedrich Bolz}
           {Heinrich-Heine-Universität Düsseldorf}
           {cfbolz@gmx.de}
\authorinfo{Maciej Fijałkowski}
           {Affiliation2}
           {fijall@gmail.com}

@@

XXX should we have a mention where in the previous papers those optimizations
are discussed? Is the previous XXX precisely about this?

@@

\subsection{Heap Caching}

XXX gcc calles this store-sinking and I'm sure there are some
references in the literature (none at hand though). This is a ``typical''
compiler optimization.

The objective of heap caching is to remove \lstinline{get} and
\lstinline{set} operations whose results can be deduced from previous
\lstinline{get} and \lstinline{set} operations. Exact details of the
process are outside the scope of this paper. We only consider the interaction
with loop peeling.
